### 2011-08-15 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

@@

\begin{verbatim}
Intel Core 2 Quad processor @ 2.83 GHz
8 GB DDR2 RAM
x86_64 GNU/Linux 2.6.32-33-generic Ubuntu 10.04
Java HotSpot 64-Bit Server VM (build 20.1-b02)
GLPK version 4.38
\end{verbatim}

@@

\begin{verbatim}
Intel Core 2 Duo processor @ 2.33 GHz
4 GB DDR2 RAM
Windows 7 SP1 64bit
Java HotSpot TODO
GLPK version TODO
\end{verbatim}

@@

\begin{table}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine           & Windows \\
  Input data set    & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
  \end{tabular}
\end{table}

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \jmodule{Glpk} CH set to a time limit from 1 to 49 seconds with increments of 2 (25 settings * 20 iterations = 500 configurations in total). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights).\\

TODO input -> time dependency too

>>>>

TODO verify they satisfy their schemas. Converted too.

@@

\begin{verbatim}
Intel Core 2 Quad processor @ 2.83 GHz
8 GB DDR2 RAM
x86_64 GNU/Linux 2.6.32-33-generic Ubuntu 10.04
Java SE Runtime Environment (build 1.6.0_26-b03)
Java HotSpot 64-Bit Server VM (build 20.1-b02)
GLPK version 4.38
\end{verbatim}

@@

\begin{verbatim}
Intel Core 2 Duo processor @ 2.33 GHz
4 GB DDR2 RAM
Windows 7 SP1 64bit
Java SE Runtime Environment (build 1.6.0_26-b03)
Java HotSpot 32-Bit Client VM (build 20.1-b02)
GLPK version 4.45 (Cygwin)
GLPK version 4.34 (native)
\end{verbatim}

@@

\begin{table}
  \caption{GLPK: native vs. Cygwin summary 1}
  \label{experiment-glpk-native-vs-cygwin-summary-1}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine           & Windows \\
  Input data set    & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
  \end{tabular}
\end{table}

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \jmodule{Glpk} CH set to a time limit from 1 to 49 seconds with increments of 2, meaning 25 settings * 20 iterations = 500 configurations in total (see listing \ref{listing-experiment-glpk-native-vs-cygwin-1}). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights).

\begin{algorithm}
\caption{GLPK: native vs. Cygwin set generation 1}
\label{listing-experiment-glpk-native-vs-cygwin-1}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 20$}
	\FOR{$time = 1 \to 49$ step $2$}
    \STATE $ES \gets ES \cup {CH = \jmodule{Glpk}(limit = time), IH = \emptyset}$  
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

TODO graph + interpretation

\begin{table}
  \caption{GLPK: native vs. Cygwin summary 2}
  \label{experiment-glpk-native-vs-cygwin-summary-2}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine           & Windows \\
  Input data set    & sized artificial data \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
  \end{tabular}
\end{table}

Another way to compare the performance of these two GLPK versions is to see how long it takes them to find the optimum for a set of data of increasing size. This experimental set will contain 220 configurations for each version. Every configuration will let \jmodule{Glpk} CH run for unlimited time, until it finds the optimum. This will be repeated in 20 iterations for each of the 11 files from the sized artificial data set (TODO link) (see listing \ref{listing-experiment-glpk-native-vs-cygwin-2}). There will again be no IH, the only data we will collect are the times of the CH run in each case.

\begin{algorithm}
\caption{GLPK: native vs. Cygwin set generation 2}
\label{listing-experiment-glpk-native-vs-cygwin-2}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 20$}
	\FOR{$file \in $ sized artificial data}
    \STATE $ES \gets ES \cup {file, CH = \jmodule{Glpk}(no limit), IH = \emptyset}$  
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

TODO graph + interpretation
